---
title: "Ex1b"
format: html
editor: visual
---

## Exercise 1b

Sample 100 values from a log-normal distribution (see the rlnorm function; you can use mu=5,sigma=0.5); using the ggplot2 package, create a histogram of the sampled data on both the linear and log scales; create also a violin plot; within your quarto document,write 1-2 sentences to describe your steps and organize the document with subsection headings; **report the mean and standard deviation of your sampled values** in line in the text.

## Solution

Install libraries and packages.

```{r}
library(reshape2)
library(ggplot2)

```

Firstly, I set the seed to have constantly the same results for rlnorm. Then I generate the samples using the function rlnorm and the given parameters. I generate two data frames with the data (df and logdf) for easier plotting. At the end I find the min, max, mean and st.dev. of the data.

```{r}

set.seed(1)
n=100
mu=5
sigma =0.5
x=rlnorm(100,meanlog=mu, sdlog=sigma)
df=data.frame(x)
logdf =data.frame(log(x))
mean(x)
sd(x)
min(x)
max(x)

```

```         
mean 172.9923
standard deviation 80.36899
```

### Histogram

Histogram of the sampled data in linear and log form using ggplot histograms.

```{r}

ggplot(df, aes(x)) +             
  geom_histogram(bins=25)
ggplot(logdf, aes(log(x))) +     
  geom_histogram(bins = 25)
```

### Violin plot

Before I can plot my violin plots, I need to reshape them. Lastly, I plot the violin plots.

```{r}
#reshaping the data
df.m <- reshape2::melt(df, id.vars = NULL)
df.n <- reshape2::melt(logdf, id.vars = NULL)
#plotting
ggplot(df.m, aes(x = variable, y = value)) + geom_violin()
ggplot((df.n), aes(x = variable, y = value)) + geom_violin()
```
